---
title: "MA615_919"
format: pdf
editor: visual
---

**Description**

This data set contains statistics, in arrests per 100,000 residents for assault, murder, and rape in each of the 50 US states in 1973. Also given is the percent of the population living in urban areas.

```{r}
library(datasets)
library(ggplot2)
library(tibble)
data("USArrests")
head(USArrests)
```

```{r}
arrests <- USArrests
ggplot(arrests, aes(x = Murder, y = Assault,color = UrbanPop)) +
  geom_point(size = 3) +
  scale_color_gradient(low='green',high = 'blue')+
  geom_smooth(method = "lm", color = "red") +
  labs(title = "Relationship Between Murder and Assault Rates",
       x = "Murder (per 100,000)",
       y = "Assault (per 100,000)",
       color = "Urban Population (%)")
```

**Conclusion**

This scatter plot shows the relationship between murder and assault rates across the 50 US states in 1973. Each point represents a state, and the color intensity reflects the rate of the population living in urban areas. lighter green indicates lower urbanization, while darker blue indicates higher urbanization. The red trend line indicates a positive association: states with higher murder rates generally tend to have higher assault rates.Besides, from the scatter plot and trend line, states with higher urbanization (darker blue) tend to have higher expected assault rates.
